---
title: "Concordance Data Summary as of 2022-12-30"
output: 
  word_document:
    reference_docx: template.docx
    toc: TRUE
    toc_depth: 2
params:
  summaryFile: Code/dataChecking/01_dataSummarizer.R
---

# Summary

-   Summary of selected variables found in the Concordance Study for cleaning of data downloaded the 30 of December 2022.

```{r setup and establish connections, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)

source(params$summaryFile)
library(magrittr)
```

```{r Basic Data Formatting}


variableNumbers <- c(3:10,24,25:26,30,59,60:70,87:90,91:101,113:143,169:202)


dataSummary <- dataDict %>% 
  slice(variableNumbers) %>%
  mutate(rep=if_else(is.na(rep),'',source),
         values=str_remove_all(values,'\"') %>% str_split(','),
         shortcats=str_remove_all(shortcats,'\"') %>% str_split(',')) %>% 
  mutate(dat=pmap(list(varnm,rep,tp,values),
                  ~getData(data=data,variableName=..1,instrumentLabel=..2,dataType=..3,values=..4)))%>% 
  mutate(dat=pmap(list(dat,tp,varnm,values,shortcats),
                  ~formatSummaryData(data=..1,dataType = ..2,variableName = ..3, variableValues = ..4,dataLabels = ..5))) %>% 
  mutate(dat=pmap(list(dat,tp),
                  ~dataCutting(..1,..2))) %>% 
  mutate(summaryOutput=pmap(list(dat,myLabel),
                            ~variableSummarizer(..1,..2)))







```

```{r Adding Full Data Tables}

#Remove extra rows from dataSummary to only include the first row from
#each source in replaceWithTable
replaceWithTable <- c('blood_biomarker_results','fup_mets_treatment')

dataSummary <- dataSummary %>% 
  group_by(source) %>% 
  mutate(rnm=row_number()) %>% 
  ungroup() %>% 
  filter(!(source%in%replaceWithTable&rnm>1)) %>% 
  select(-rnm)



getDataFullTable <- function(data,dataDict,instrumentLabel){
  
  instrumentVariables <- dataDict %>% 
    filter(source==instrumentLabel) %>%
    pull(varnm)
  
  newVariableNames <- dataDict %>% 
    filter(source==instrumentLabel) %>%
    pull(myLabel)
  
  renameList <- setNames(instrumentVariables,newVariableNames)
  
  returnDat <- data %>% 
    filter(redcap_repeat_instrument%in%instrumentLabel) %>% 
    select(ord,vis_id,all_of(instrumentVariables)) %>% 
    rename(!!renameList)
  
  return(returnDat)
}

formTable <- function(formData,source){
  
  summaryTable <- formData %>%
    select(-ord) %>% 
    arrange(vis_id) %>% 
    mutate(vis_id=as.character(vis_id)) %>% 
    flextable() %>% 
    add_header_row(values=source,colwidths = (ncol(formData)-1)) %>% 
    width(c(1:(ncol(formData)-1)),width=7/(ncol(formData)-1)) %>% 
    bg(i=seq(1,nrow(formData),2),bg='grey90')
  
  return(summaryTable)
}


replacementTables <- dataSummary %>% 
  filter(source%in%replaceWithTable) %>% 
  unnest(summaryOutput) %>% 
  mutate(dat=map(source,
                 ~getDataFullTable(data,dataDict,.x)),
         summaryTable=map2(dat,source,
                           ~formTable(.x,.y)),
         myLabel='Data Table',
         graphic='defaultTable') %>% 
  nest(summaryOutput=c(summaryPlot,summaryTable,lowCountIds))


#SummaryOutput=summaryPlot,summaryTable,lowCountIds

dataSummary <- dataSummary %>%
  rows_update(replacementTables, by='ord')


```


```{r Adding specific Tables}

compareSurgDates <- function(data){
  summaryTable <- data %>% 
    filter(redcap_repeat_instrument=='') %>% 
    select(vis_id,vis_dobiop,cor_dobiop) %>% 
    mutate(vis_dobiop = as.character(vis_dobiop) %>% ymd(),
           cor_dobiop = as.character(cor_dobiop) %>% ymd()) %>% 
    filter(!(vis_dobiop==cor_dobiop)|is.na(vis_dobiop)|is.na(vor_dobiop)) %>% 
    flextable() %>% 
    add_header_row(values=source,colwidths = (ncol(formData)-1)) %>% 
    width(c(1:(ncol(formData)-1)),width=7/(ncol(formData)-1)) %>% 
    bg(i=seq(1,nrow(formData),2),bg='grey90')
  
  return(summaryTable)
}

concatinatedDataTable <- function(data, dataDict){
  
  groupedVars <- c('cor_onctrt_asmets','cor_onctrt_erpos','cor_onctrt_herpos','cor_onctrt_tn')
  groupedSyms <- groupedVars %>% 
    map(as.symbol)
  

  
  summaryData <- data %>% 
    filter(redcap_repeat_instrument=='') %>% 
    select(vis_id,all_of(groupedVars)) %>% 
    group_by(!!!groupedSyms) %>%
    mutate(vis_id=as.character(vis_id)) %>% 
    summarise(firstID=as.numeric(first(vis_id)),
              vis_id=str_flatten(vis_id,', '),.groups = 'drop') %>% 
    ungroup() %>% 
    arrange(firstID) %>% 
    select(vis_id,all_of(groupedVars)) 
  
  
  renameList <- dataDict %>% 
    filter(varnm%in%groupedVars)%$%
    setNames(varnm,myLabel)
  
  summaryTable <- summaryData %>% 
    rename(!!renameList) %>% 
    flextable() %>% 
    add_header_row(values='Treatment Plan Details',colwidths = (ncol(summaryData))) %>% 
    width(1,2) %>% 
    width(c(2:(ncol(summaryData))),width=5/(ncol(summaryData)-1)) %>%
    bg(i=seq(1,nrow(summaryData),2),bg='grey90')
  
  return(summaryTable)
}


# data %>% 
#   concatinatedDataTable(dataDict)




```



```{r Document Creation, results='asis'}



sectionKnit <- function(x){
  knitr::knit_child(text = c(
    '## `r filter(dataSummary,varnm==x) %>% pull(myLabel)`',
    '',
    '```{r}',
    'summaryRow <- dataSummary %>%
    filter(varnm == x) %>% 
    unnest(summaryOutput)',
    '',
    'switch(summaryRow$graphic,
    defaultPlot=summaryRow %>% pull(summaryPlot),
    defaultTable=summaryRow %>% pull(summaryTable)) %>% 
    .[[1]]',
    '```',
    ''
  ), envir = environment(), quiet = TRUE)
}

formKnit <- function(form){
  # knitr::knit_child(param$knitChildFile, envir = environment(), quiet = TRUE)
  knitr::knit_child(text = c(
    '```{r}',
    'isRepeated <- dataDict %>% 
    filter(source == form) %>% 
    slice(1) %>% 
    pull(rep) %>% 
    {!is.na(.)}',
    'formName <- form %>% str_replace_all("_"," ") %>% str_to_title()',
    'if(isRepeated){',
      'formName <- paste0(formName," (Repeated Form)")',
    '}',
    '```',
    '',
    '# `r formName`',
    '',
    '```{r, results="asis"}',
    'sectionRes <- dataSummary %>%
    filter(source == form) %>%
    pull(varnm) %>%
    map(sectionKnit)\n',
    'cat(unlist(sectionRes), sep = "\n")',
    '```',
    ''
  ), envir = environment(), quiet = TRUE) %>% 
    return()
}


res <- dataSummary %>% 
  distinct(source) %>% 
  pull(source) %>% 
  map(formKnit)
  
cat(unlist(res), sep = '\n')

```
