---
title: "Concordance Data Summary as of 2022-12-30"
output: 
  word_document:
    reference_docx: template.docx
    toc: TRUE
    toc_depth: 2
params:
  summaryFile: Code/dataChecking/01_dataSummarizer.R

---

# Summary
-   Summary of selected variables found in the Concordance Study for cleaning of data downloaded the 30 of December 2022.

```{r setup and establish connections, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)

source(params$summaryFile)

```



```{r documentCreation, results='asis'}



sectionKnit <- function(x){
  knitr::knit_child(text = c(
    '## `r filter(dataSummary,varnm==x) %>% pull(myLabel)`',
    '',
    '```{r}',
    'summaryRow <- dataSummary %>%
    filter(varnm == x) %>% 
    unnest(summaryOutput)',
    '',
    'switch(summaryRow$graphic,
    defaultPlot=summaryRow %>% pull(summaryPlot),
    defaultTable=summaryRow %>% pull(summaryTable)) %>% 
    .[[1]]',
    '```',
    ''
  ), envir = environment(), quiet = TRUE)
}

formKnit <- function(form){
  # knitr::knit_child(param$knitChildFile, envir = environment(), quiet = TRUE)
  knitr::knit_child(text = c(
    '```{r}',
    'isRepeated <- dataDict %>% 
    filter(source == form) %>% 
    slice(1) %>% 
    pull(rep) %>% 
    {!is.na(.)}',
    'formName <- form %>% str_replace_all("_"," ") %>% str_to_title()',
    'if(isRepeated){',
      'formName <- paste0(formName," (Repeated Form)")',
    '}',
    '```',
    '',
    '',
    '',
    '# `r formName`',
    '',
    '```{r, results="asis"}',
    '',
    '',
    '',
    
    'sectionRes <- dataSummary %>%
    filter(source == form) %>%
    pull(varnm) %>%
    map(sectionKnit)\n',
    'cat(unlist(sectionRes), sep = "\n")',
    '```',
    ''
  ), envir = environment(), quiet = TRUE) %>% 
    return()
}


res <- dataSummary %>% 
  distinct(source) %>% 
  pull(source) %>% 
  map(formKnit)
  
cat(unlist(res), sep = '\n')

```

